Sample size

### 2021-04-18 scripts/r/sample-size/sample-size.Rmd
:zap: - use weak priors and set seed

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
theme_set(theme_light(base_family = "Lato"))
library(brms)
library(extraDistr)
library(HDInterval)
library(tidybayes)
```

@@

set.seed(99)

priors <- c(
  prior(normal(2, 2), class = Intercept),
  prior(cauchy(0, 1), class = sd)
)

# run simple model
silber_sd <- brm(
  z_score ~ (1 | Team),
  data = silber,
  prior = priors,
  chain = 4,
  iter = 4000,
  cores = 4,
  #backend = "cmdstanr", threads = threading(4),
  control = list(adapt_delta = 0.99999999, max_treedepth = 15),
  file = "./models/sims/silber_sd"
)

@@

run_brm <- function(data) {
  priors <- c(
    brms::prior(normal(0, 1), class = Intercept),
    brms::prior(cauchy(0, 1), class = sd)
  )

  meta_bm <- brms::brm(
    z_score ~
      (1 | team),
    data = data,
    prior = priors,
    chain = 4,
    iter = 6000,
    cores = 4,
    backend = "cmdstanr", threads = brms::threading(4),
    control = list(adapt_delta = 0.9999, max_treedepth = 15),
  )

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
theme_set(theme_light(base_family = "Lato"))
library(brms)
library(extraDistr)
library(HDInterval)
library(tidybayes)
my_seed <- 99
```

@@

priors <- c(
  prior(normal(0, 3), class = Intercept),
  prior(cauchy(0, 1), class = sd)
)

# run simple model
silber_sd <- brm(
  z_score ~ (1 | Team),
  data = silber,
  prior = priors,
  chain = 4,
  iter = 4000,
  cores = 4,
  seed = my_seed,
  backend = "cmdstanr", threads = threading(4),
  control = list(adapt_delta = 0.9999, max_treedepth = 15),
  file = "./models/sims/silber_sd"
)

@@

run_brm <- function(data) {
  priors <- c(
    brms::prior(normal(0, 3), class = Intercept),
    brms::prior(cauchy(0, 1), class = sd)
  )

  meta_bm <- brms::brm(
    z_score ~
      (1 | team),
    data = data,
    prior = priors,
    chain = 4,
    iter = 6000,
    cores = 4,
    seed = my_seed,
    backend = "cmdstanr", threads = brms::threading(4),
    control = list(adapt_delta = 0.9999, max_treedepth = 15),
  )
